Evaluation of the repository

### 2024-09-09 pages/paper_evaluation.qmd
feat(evaluation): add kim 2021

<!-- TODO: Add Johnson et al. 2021 and Kim et al. 2021 -->

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 6, 3, 1],
  'Lim et al. 2020': [16, 2, 3, 3],
  'Kim et al. 2021': [0, 0, 0, 1],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
ispor_dict = {
  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
  'Huang et al. 2019': [7, 2, 7, 2],
  'Lim et al. 2020': [12, 0, 4, 2],
  'Kim et al. 2021': [0, 0, 0, 1],
  'Anagnostou et al. 2022': [8, 3, 4, 3],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
ispor_wide = pd.DataFrame(ispor_dict, index=col).T

@@

| **2.1 Base model overview diagram**<br>Describe the base model using appropriate diagrams and description.  This could include one or more process flow, activity cycle or equivalent diagrams sufficient to describe the model to readers.  Avoid complicated diagrams in the main text.  The goal is to describe the breadth and depth of the model with respect to the system being studied. | ✅ | ✅ | ✅ | tbc | ✅ |
| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | tbc | ✅ |

@@

| **2.4 Algorithms**<br>Provide further detail on any algorithms in the model that (for example) mimic complex or manual processes in the real world (i.e.  scheduling of arrivals/ appointments/ operations/ maintenance, operation of a conveyor system, machine breakdowns, etc.). Sufficient detail should be included (or referred to in other published work) for the algorithms to be reproducible.  Pseudo-code may be used to describe an algorithm. | ✅ | 🟡 | ✅ | tbc | ✅ |

@@

| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | tbc | ✅ |
| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | tbc | ✅ |
| **2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g. First in First Out, Last in First Out, prioritisation, etc.). Where one or more queues have a different discipline from the rest, provide a list of queues, indicating the queuing discipline used for each.  If reneging, balking or jockeying occur, etc., provide details of the rules. Detail any delays or capacity constraints on the queues. | ✅ | ✅ | N/A | tbc | ✅ |

@@

| **4.1 Initialisation**<br>Report if the system modelled is terminating or non-terminating.  State if a warm-up period has been used, its length and the analysis method used to select it.  For terminating systems state the stopping condition.<br>State what if any initial model conditions have been included, e.g., pre-loaded queues and activities.  Report whether initialisation of these variables is deterministic or stochastic. | 🟡 | ❌ | ❌ | tbc | ❌ |

@@

| **5.3 Model execution**<br>State the event processing mechanism used e.g. three phase, event, activity, process interaction.<br>*Note that in some commercial software the event processing mechanism may not be published. In these cases authors should adhere to item 5.1 software recommendations.*<br>State all priority rules included if entities/activities compete for resources.<br>If the model is parallel, distributed and/or use grid or cloud computing, etc., state and preferably reference the technology used.  For parallel and distributed simulations the time management algorithms used.  If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | tbc | ❌ |
| **5.4 System specification**<br>State the model run time and specification of hardware used.  This is particularly important for large scale models that require substantial computing power.  For parallel, distributed and/or use grid or cloud computing, etc. state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | tbc | ❌ |

@@

<!-- TODO: Add Johnson and amend Kim after discussion if required -->

@@

| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | tbc | ✅ |

@@

<!-- Add johnson and kim -->

* @shoaib_simulation_2021 - 1h 56m
* @huang_optimizing_2019 - 1h 28m
* @lim_staff_2020 - 1h 12m
* @kim_modelling_2021
* @anagnostou_facs-charm_2022 - 53m
* @johnson_cost_2021

>>>>

<!-- TODO: Add Johnson et al. 2021 -->

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 6, 3, 1],
  'Lim et al. 2020': [16, 2, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
ispor_dict = {
  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
  'Huang et al. 2019': [7, 2, 7, 2],
  'Lim et al. 2020': [12, 0, 4, 2],
  'Kim et al. 2021': [12, 0, 5, 1],
  'Anagnostou et al. 2022': [8, 3, 4, 3],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
ispor_wide = pd.DataFrame(ispor_dict, index=col).T

@@

| **2.1 Base model overview diagram**<br>Describe the base model using appropriate diagrams and description.  This could include one or more process flow, activity cycle or equivalent diagrams sufficient to describe the model to readers.  Avoid complicated diagrams in the main text.  The goal is to describe the breadth and depth of the model with respect to the system being studied. | ✅ | ✅ | ✅ | ✅ | ✅ |
| **2.2 Base model logic**<br>Give details of the base model logic. Give additional model logic details sufficient to communicate to the reader how the model works. | ✅ | ✅ | ✅ | ✅ | ✅ |

@@

| **2.4 Algorithms**<br>Provide further detail on any algorithms in the model that (for example) mimic complex or manual processes in the real world (i.e.  scheduling of arrivals/ appointments/ operations/ maintenance, operation of a conveyor system, machine breakdowns, etc.). Sufficient detail should be included (or referred to in other published work) for the algorithms to be reproducible.  Pseudo-code may be used to describe an algorithm. | ✅ | 🟡 | ✅ | 🟡 | ✅ |

@@

| **2.5.2 Components - activities**<br>Describe the activities that entities engage in within the model. Provide details of entity routing into and out of the activity. | ✅ | ✅ | ✅ | ✅ | ✅ |
| **2.5.3 Components - resources**<br>List all the resources included within the model and which activities make use of them. | ✅ | ✅ | N/A | N/A | ✅ |
| **2.5.4 Components - queues**<br>Give details of the assumed queuing discipline used in the model (e.g. First in First Out, Last in First Out, prioritisation, etc.). Where one or more queues have a different discipline from the rest, provide a list of queues, indicating the queuing discipline used for each.  If reneging, balking or jockeying occur, etc., provide details of the rules. Detail any delays or capacity constraints on the queues. | ✅ | ✅ | N/A | N/A | ✅ |

@@

| **4.1 Initialisation**<br>Report if the system modelled is terminating or non-terminating.  State if a warm-up period has been used, its length and the analysis method used to select it.  For terminating systems state the stopping condition.<br>State what if any initial model conditions have been included, e.g., pre-loaded queues and activities.  Report whether initialisation of these variables is deterministic or stochastic. | 🟡 | ❌ | ❌ | 🟡 | ❌ |

@@

| **5.3 Model execution**<br>State the event processing mechanism used e.g. three phase, event, activity, process interaction.<br>*Note that in some commercial software the event processing mechanism may not be published. In these cases authors should adhere to item 5.1 software recommendations.*<br>State all priority rules included if entities/activities compete for resources.<br>If the model is parallel, distributed and/or use grid or cloud computing, etc., state and preferably reference the technology used.  For parallel and distributed simulations the time management algorithms used.  If the HLA is used then state the version of the standard, which run-time infrastructure (and version), and any supporting documents (FOMs, etc.) | 🟡 |❌ | ❌ | ❌ | ❌ |
| **5.4 System specification**<br>State the model run time and specification of hardware used.  This is particularly important for large scale models that require substantial computing power.  For parallel, distributed and/or use grid or cloud computing, etc. state the details of all systems used in the implementation (processors, network, etc.) | ✅ | ❌ | 🟡 | 🟡 | ❌ |

@@

<!-- TODO: Add Johnson -->

@@

| **3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation. | ✅ | ✅ | ✅ | ✅ | ✅ |

@@

<!-- TODO: Add johnson -->

* @shoaib_simulation_2021 - 1h 56m
* @huang_optimizing_2019 - 1h 28m
* @lim_staff_2020 - 1h 12m
* @kim_modelling_2021 - 2h 12m
* @anagnostou_facs-charm_2022 - 53m
* @johnson_cost_2021

### 2024-09-09 pages/repo_evaluation.qmd
feat(evaluation): add kim 2021

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
  'Huang et al. 2019': [3, 0, 9, 0],
  'Lim et al. 2020': [3, 0, 9, 0],
  'Kim et al. 2021': [0, 0, 0, 1],
  'Anagnostou et al. 2022': [10, 0, 2, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badge_dict = {
  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
  'Huang et al. 2019': [0, 0, 12, 0],
  'Lim et al. 2020': [3, 0, 9, 0],
  'Kim et al. 2021': [0, 0, 0, 1],
  'Anagnostou et al. 2022': [5, 0, 7, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
badge_wide = pd.DataFrame(badge_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
essential_dict = {
  'Shoaib and<br>Ramamohan 2021': [2, 0, 6, 0],
  'Huang et al. 2019': [2, 0, 6, 0],
  'Lim et al. 2020': [2, 0, 6, 0],
  'Kim et al. 2021': [0, 0, 0, 1],
  'Anagnostou et al. 2022': [7, 0, 1, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
essential_wide = pd.DataFrame(essential_dict, index=col).T

@@

```{python}
# Create dataframe of results
optional_dict = {
  'Shoaib and<br>Ramamohan 2021': [0, 0, 5, 0],
  'Huang et al. 2019': [2, 0, 3, 0],
  'Lim et al. 2020': [0, 0, 5, 0],
  'Kim et al. 2021': [0, 0, 0, 1],
  'Anagnostou et al. 2022': [1, 1, 3, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
optional_wide = pd.DataFrame(optional_dict, index=col).T

@@

<!-- Add johnson and kim -->

* @shoaib_simulation_2021 - 30m
* @huang_optimizing_2019 - 17m
* @lim_staff_2020 - 18m
* @kim_modelling_2021
* @anagnostou_facs-charm_2022 - 19m
* @johnson_cost_2021

>>>>

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
  'Huang et al. 2019': [3, 0, 9, 0],
  'Lim et al. 2020': [3, 0, 9, 0],
  'Kim et al. 2021': [5, 0, 7, 0],
  'Anagnostou et al. 2022': [10, 0, 2, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badge_dict = {
  'Shoaib and<br>Ramamohan 2021': [3, 0, 9, 0],
  'Huang et al. 2019': [0, 0, 12, 0],
  'Lim et al. 2020': [3, 0, 9, 0],
  'Kim et al. 2021': [3, 0, 9, 0],
  'Anagnostou et al. 2022': [5, 0, 7, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
badge_wide = pd.DataFrame(badge_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
essential_dict = {
  'Shoaib and<br>Ramamohan 2021': [2, 0, 6, 0],
  'Huang et al. 2019': [2, 0, 6, 0],
  'Lim et al. 2020': [2, 0, 6, 0],
  'Kim et al. 2021': [4, 1, 3, 0],
  'Anagnostou et al. 2022': [7, 0, 1, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
essential_wide = pd.DataFrame(essential_dict, index=col).T

@@

```{python}
# Create dataframe of results
optional_dict = {
  'Shoaib and<br>Ramamohan 2021': [0, 0, 5, 0],
  'Huang et al. 2019': [2, 0, 3, 0],
  'Lim et al. 2020': [0, 0, 5, 0],
  'Kim et al. 2021': [0, 0, 5, 0],
  'Anagnostou et al. 2022': [1, 1, 3, 0],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
optional_wide = pd.DataFrame(optional_dict, index=col).T

@@

* @shoaib_simulation_2021 - 30m
* @huang_optimizing_2019 - 17m
* @lim_staff_2020 - 18m
* @kim_modelling_2021 - 18m
* @anagnostou_facs-charm_2022 - 19m
* @johnson_cost_2021
